Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-29 paper/testing.tex
More wordsmithing in beginning of Testing section

Before discussing the final steps in synthesis, we take a moment to
discuss how code contracts, and any AGREE specification in general, can be traditionally tested to build assurance.
Writing and proving properties about AGREE specifications is hard not just because it is a formal process but  because it reasons about constraints that define the entire input space for a component, and the entire output space, at once.
The case studies showed that engineers, and formal method practitioners, make mistakes writing these specifications especially if the computation or temporal reasoning is complex.

>>>>

Before discussing the final steps in synthesis, we take a moment to
discuss how code contracts, and any AGREE specification in general, can be traditionally tested to build assurance.
Writing and proving properties about AGREE specifications is difficult not just because it is a formal process but because it reasons about constraints that define the entire input space for a component, and the entire output space, at once.
Case studies have shown that engineers, as well as formal method practitioners, make mistakes writing these specifications, especially if the computation or temporal reasoning is complex.
